% Ubah judul dan label berikut sesuai dengan yang diinginkan.
\section{Pose Estimation}
\label{sec:poseestimation}

% Ubah paragraf-paragraf pada bagian ini sesuai dengan yang diinginkan.

\subsection{Pose Estimation}
\label{subsec:poseestimation}

Pose estimation is a heavily explored area with applications in gaming, animation, action recognition, activity tracking, and augmented reality.
In order to improve pose estimate outcomes, various approaches have been developed. These methods may generally be split into: single-person and multi-person approaches.
The single-person approach is fundamentally a regression issue because it just determines the pose of a single person in an image, 
the person's position and an implicit number of keypoints are already known. However, the multi-person approach tries to solve an unconstrained problem because we do not know 
the positions and number of persons within the image, therefore the framework has to detect keypoints and assemble an unknown number of persons \citep{romeo}.

\subsection{Human and Humanoid Robot Pose Estimation}
\label{subsec:uhmanandrobotposeestimation}

Pose estimation on humans can be divided into two techniques: 2D Pose Estimation and 3D Pose Estimation.
2D pose estimation is a type of pose estimation that can estimate the locations of the body joints in 2D space relative to input data (i.e., image or video frame). 
The location is represented in \emph{x, y} coordinates for each key point. On the other hand, 3D pose estimation transforms a 2D image into a 3D object by estimating an additional Z-dimension to the prediction.
3D pose estimation enables us to predict the accurate spatial positioning of a represented person or thing.
Humanoid robots and persons have similar shapes, which has both advantages and disadvantages. On the one hand, this allows us to start with approaches already in use for persons,
but on the other, it makes it harder for us to distinguish between persons and humanoid robots \citep{amini2021}.